Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-22 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

On the other hand, it is easy to verify that $\bar{\mu}_{1}$ is convex.
Every state is consistent with $\bar{\mu}_{1}$, in particular $\proj{0}$
and $\proj{1}$. It is easy to see 
\begin{eqnarray*}
\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{1}}=-1\textrm{ ,}\\
\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{0}}=1\textrm{ ,}
\end{eqnarray*}
which is consistent with the theorem.

In contrast to the usual identity~$\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\rho}=\expval{\mathbf{O}_{1}}_{\rho}+\expval{\mathbf{O}_{2}}_{\rho}$,
we have
\[
\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\ne\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
\]
because the precision is easily be lost when applying arithmetic operations.

>>>>

On the other hand, it is easy to verify that $\bar{\mu}_{1}$ is convex.
Every state is consistent with $\bar{\mu}_{1}$, in particular $\proj{0}$
and $\proj{1}$. It is easy to see\begin{subequations}
\begin{eqnarray}
\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{1}}=-1\textrm{ ,}\\
\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho} & = & \expval{\sigma_{\mathrm{z}}}_{\proj{0}}=1\textrm{ ,}
\end{eqnarray}
\end{subequations}which is consistent with the theorem.

In contrast to the usual identity~$\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\rho}=\expval{\mathbf{O}_{1}}_{\rho}+\expval{\mathbf{O}_{2}}_{\rho}$,
we have
\begin{equation}
\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\subsetneq\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
\end{equation}
because the precision is easily be lost when applying arithmetic operations.
In general, when $\bar{\mu}$ is convex, we have 
\begin{equation}
\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{.}
\end{equation}
